SOBP_Analyses_BHRC_ABCD_ACEsCog

### 2021-11-18 SOBP_Analyses_BHRC_ABCD_ACEsCog.Rmd
bonferroni correction and moderation effects
Updated bonferroni correction to include adjusted p-values, and added analysis of moderation effects with sex in ABCD dataset.

abcd.long.complete <- abcd.long[complete.cases(abcd.long[,c("CogType","CogScore","ACEsType","ACEsScore")]),c("CogType","CogScore","ACEsType","ACEsScore")]

@@

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))

summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))

summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))

>>>>

abcd.long.complete <- abcd.long[complete.cases(abcd.long[,c("CogType","CogScore","ACEsType","ACEsScore")]),c("CogType","CogScore","ACEsType","ACEsScore","interview_age","sex","rel_family_id")]

@@

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
p.adjust(c(0.615, 2e-16,0.035,6.96e-11),method="bonferroni")

summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
p.adjust(c(0.389, 7.47e-15,0.0096,4.39e-7),method="bonferroni")

summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+monitoring.binary+abuse.binary+trauma.binary,data=abcd.data))
p.adjust(c(0.034, 2e-16,0.014,6.18e-8),method="bonferroni")

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+monitoring.binary+monitoring.binary*sex,data=abcd.data))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+abuse.binary+abuse.binary*sex,data=abcd.data))

summary(lmer(thompson_PC1~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
summary(lmer(thompson_PC2~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))
summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+trauma.binary+trauma.binary*sex,data=abcd.data))

summary(lmer(thompson_PC3~interview_age+sex+(1|rel_family_id)+acceptance.binary+acceptance.binary*sex,data=abcd.data))

summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+acceptance.binary+CogType+CogType*acceptance.binary,data=data.long))
summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+monitoring.binary+CogType+CogType*monitoring.binary,data=data.long))
summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+abuse.binary+CogType+CogType*abuse.binary,data=data.long))
summary(lmer(CogScore~interview_age+sex+(1|rel_family_id)+trauma.binary+CogType+CogType*trauma.binary,data=data.long))
